ISEC_abstract

### 2021-12-09 doc/isec_abstract.Rmd
clarify owl model

We provide a general overview of the package structure, and demonstrate features using several examples (Snowy Owl distribution in North America, and a dataset describing the distribution of Pacific cod in British Columbia).

>>>>

We provide a general overview of the package structure, and demonstrate features using several examples (Snowy Owl winter irruptions in North America, and a dataset describing the distribution of Pacific cod in British Columbia).
